%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Consultant (full-time)} % Job title
  {Dekimo Experts Gent} % Organization
  {Gent, Belgium} % Location
  {July 2023~\textendash~Present} % Date(s)
  {}

%---------------------------------------------------------
  \cventry
  {Expert RTL Designer (full-time)} % Job title
  {Sony Depthsensing Solutions (SDS)} % Organization
  {Brussels, Belgium} % Location
  {January 2025~\textendash~July 2025} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and optimized a real-time CSI-2 packet to ASEP packet converter system with fragmentation for transmission, achieving minimal latency and without data buffering with SystemVerilog and Cadence Xcelium (SystemVerilog)}
      \item {Collaborated in a team environment utilizing Bitbucket for source control, Confluence for documentation, and Jira for task and sprint planning.}
      \item {Working with the verification team to design tests for system debugging using Universal Verification Methodology (UVM with SystemVerilog)}
      \item {\textbf{Improved skills}: SystemVerilog, Digital design, UVM libraries}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Expert RTL Designer (full-time)} % Job title
  {CarUX} % Organization
  {Heerlen, Netherlands } % Location
  {July 2023~\textendash~November 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and optimized a complete controller system based on the Nios II processor on Intel FPGAs with a wide variety of prepherals (SD card reader, DDR4, I2C, UART, etc)}
      \item {Developed a video stream generator system based on DisplayPort on Intel FPGAs using Multi-Stream Transport (MST) for transmission of high-resolution video streams in VHDL.}
      \item {Implemented a video stream transmitter based on DisplayPort with Display Stream Compression (DSC), live compressor, and playback pre-compressed image loader for high-resolution images in VHDL.}
      \item {Merge the system controller with MST (3 streams plus DSC compression) and enable HDCP v2.3 in one project (partially implemented in C and partially in VHDL).}
      \item {\textbf{Improved skills}: VHDL for RTL design, C for drivers on NIOS II.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Expert Embedded Firmware Developer (full-time)} % Job title
    {Sina Innovative Communication Systems} % Organization
    {Tehran, Iran} % Location
    {May 2021~\textendash~June 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Interfaces Development Based on Command Line Interface (CLI) and SNMP protocol for Optical Network Systems (as a team member refactor most of Cisco 4120 commands on the company’s new product) with C language.}
	\item {Developed, maintained, and debugged framing, mapping, and multiplexing codes of optical framer chips and modules (as a team member in charge of development and maintenance in the new kernel version).}
        \item {Implemented and modified FPGA codes on optical telecommunication cards.}
	\item {Developed Linux drivers and apps for boards with the Yocto project and Jenkins pipeline.}
	\item {Collaborated in a team environment utilizing GitLab for source control, Confluence for documentation, and Jira for task and sprint planning.}
	\item {\textbf{Improved skills}: C for development of libraries and applications, Yocto project, Linux.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Consultant and Expert Embedded System Developer (part-time)} % Job title
    {Simorgh Intelligent Sky} % Organization
    {Tehran, Iran} % Location
    {September 2020~\textendash~March 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementation of GPS and GLONASS acquisition and tracking algorithms on Zynq7020 based on FreeRTOS and Max2769 (partially implemented in C and partially in VHDL) 
 sweep 32 satellites with 82 frequencies).}
        \item {GPS anti-jamming implementation on Zynq7020 based on embedded Linux, AD9361, LTC2174, and NT1065 (partially implemented in C and partially in VHDL).}
	\item {Optimization of mentioned algorithms in MATLAB by cooperation with the system designer to achieve the optimal solution, to implement on PL and PS parts of Zynq.}
        \item {\textbf{Improved skills}: C for development of drivers, libraries, and applications. VHDL for RTL design, Petalinux and Linux kernel and drivers configuration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Midlevel Embedded Firmware and Hardware Developer (full-time)} % Job title
    {Yasin Engineering developers Co} % Organization
    {Tehran, Iran} % Location
    {September 2017~\textendash~May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Customization and configuration of embedded Linux for designed boards based on ZynqMP and K2H with C.}
	\item {Linux driver customization and development based on device tree: KSZ9893 and Si5341 with C.}
	\item {Developed a PCIe IP speed testing project on Xilinx FPGA with VHDL.}
	\item {Upgrade SATA2 to SATA3 HDL code based on 7 series Xilinx FPGAs with 470MB/s write rate with VHDL.}
	\item {SRIO (4x6Gb/s) and EMIF (16x200Mb/s) link Development between K2H and XCKU115 based on RTOS (partially implemented in C and partially in VHDL)}
	\item {10G link development on ZynqMP based on VPX protocols with almost 8Gb/s data rate (partially implemented in C and partially in VHDL)}
	\item {Development si5341 configuration code on ZynqMP FSBL to solve Highspeed IPs’ clock demands in PL in C.}
	\item {Optimization and development of algorithms (MUSIC) on K2H by OpenCL (CBLAS and LAPACK libs).}
	\item {Configuration ADC ICs by STM32 and Atmel microcontrollers (AD9680) with C.}
	\item {Performed board bring-up for FPGA/SoC-based hardware integrating high-speed ADCs.}
	\item {\textbf{Improved skills}: C for development of drivers, libraries, and applications. VHDL for RTL design.}
      \end{cvitems}
    }
    
%---------------------------------------------------------

\end{cventries}
