%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\newpage
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % projects
    {Other projects:} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Design a Xen hypervisor system on ZynqMP based on a Dom0 Linux kernel and one DomU guest kernel with an NFS filesystem (Self-study).}
        \item {Implementation of configuration and transfer data from ADC to PC by TCP protocol based on FPGA (Personal project).}
        \item {Design a target detector radar simulator on MATLAB GUI based on Adaptive Pulse Compression Algorithms (Personal project).}
        \item {Design and implementation of adaptive pulse compression algorithms on Matlab and FPGAs using Vivado HLS (Personal project).}
	\item {Tutored a workshop on "Hands-on TI keystone II processors" in Iran Electronics Industries (Introduction of ProcessorSDKs, config, modify and compile of the kernel, U-boot, drivers and kernel modules, examples about OpenCL, OpenMP, Cblas and LAPACK, Some topics about TI-RTOS) (Contract project).}
	\item {Created a TCP network between 13 client boards and two server boards with STM32H750 microcontrollers (With STM32CubeIDE and LwIP library). A computer program was designed as a client with LabVIEW that sent configuration board data to the config server. Alarms were sent to the other server with C (Contract project).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
