%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Skills}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}

%------------------------------------------------

\cvskill
{Hardware Development} % Category
{
\item[$\bullet$] Proficient in RTL design with VHDL and SystemVerilog targeting Xilinx and Intel FPGA platforms.
\item[$\bullet$] Skilled at identifying and resolving common HDL design issues such as timing violations and lint errors.
\item[$\bullet$] Proficient in addressing debugging, testing, simulation, and board bring-up challenges throughout the HDL design and deployment process.
\item[$\bullet$] Familiar with Analog Devices ADCs, STM32, and Atmel microcontrollers and their peripherals configuration (UART, I2C, SPI, and etc).
}

%------------------------------------------------

\cvskill
{System Development} % Category
{
\item[$\bullet$] Development and customization of Linux kernel, U-Boot, RTOS and firmware on Xilinx and TI SoCs (Zynq, ZynqMP, Keystone I\&II and Sitara).
\item[$\bullet$] Familiar with Linux devicetree structure and development driver in kernel.
\item[$\bullet$] Experienced with the Yocto Project build system, rootfs customization, and Jenkins CI/CD pipeline.
\item[$\bullet$] Had a study on network concepts and protocols such as TCP/IP.
}

%------------------------------------------------

\cvskill
{Softwares} % Category
{
\item[$\bullet$] C, VHDL, SystemVerilog, MATLAB, Yocto Project, OpenCl, Git, crosstool-NG
\item[$\bullet$] Familiar with C++, OOP, Python, SQLite, CMake, UVM, Xen hypervisor
}
%------------------------------------------------

\cvskill
{Personal Skills} % Category
{
\item[$\bullet$] Punctuality, Teamwork, Flexibility, and Adaptability
\item[$\bullet$] Skilled in Agile methodologies with hands-on use of JIRA, Confluence, Bitbucket, and GitLab for project management and version control
}
%------------------------------------------------

\cvskill
{Languages} % Category
{\item[$\bullet$] Persian (native), English (fluent)} % Skills

%------------------------------------------------

\end{cvskills}
